\documentclass{article}
\usepackage{graphicx}

\begin{document}

\begin{titlepage}
	\begin{center}
		\line(1,0){300} \\
			\huge{European University Cyprus}\\
				[2.25mm]
				\large{CSC230: SYSTEMS ANALYSIS \& DESIGN}\\
					\huge{CourseWork 1} \\
					[14cm]
	\end{center}
	
		\begin{flushright}
			\large {Jesse Princewill \\
				Omran Alismael\\
				Ogidan Oluwole Olukayode\\
				October 20, 2018 \\}
		\end{flushright}
\end{titlepage}
	
	\begin{center}
		\textbf{\large EUROPEAN UNIVERSITY CYRPUS \\
			DEPARTMENT OF COMPUTER SCIENCE \\
			SYSTEM REQUEST - UNIVERSITY ONLINE LIBRARY \\}
	\end{center}
\textbf{Project sponsor:} \\
[2.25mm]
\textbf{Business Needs:} This project has been initiated to reach students and teachers who are unable to reach the University library and by remaking {\textit {limited edition}} and also all books contained in the library into ebooks. it would also serve non EUC students who need access to our great variety of books however, they might be charged a fee. this project would also sell books at a cheaper price to EUC students who have a library membership\\
[2.25mm]
\textbf{Business Requirements:}\\
Using the Web, Students and Teachers of European university should be able to acquire a library membership, search, access and purchase books and also articles contained at the university Library. They should also be able to reserve the physical copy of a certain book which they intend to come pick up. \\
[2.25mm]
\textbf{System Functionality:}
\begin {itemize}
\item Categorise books into different sections (Science, Business, Medicine).
\item Search through each specified category.
\item Issue out memberships to students and teachers.
\item Keep record of each memberships purchased daily, weekly and monthly.
\item Identify wether or not a physical copy of a book is available and when it would be available.
\item Pre order a copy of a book before arrival.
\item Reserve a physical copy of a book for collection within a certain period of time.
\item Send confirmation of any reservations made.\\
\end{itemize}
\textbf{Business Values:}
We are predicting that these library memberships should get students and teachers more involved in University activities and also provide an answer as to where a certain book required for a course completion can be bought. We are also predicting that by reducing the prices of these books to 20\% less than retail price more students would be persuaded to purchase their course books from the library. Furthermore with an online presence and also the ability to purchase these books at a lower price we in turn increase awareness not only among EUC students but also our direct and indirect competitors. 
\newpage
Conservative estimates of tangible value to the company include:
\begin{itemize}
\item \$5 monthly for students (5,000 students, \$5 annually \$300,000) increase inventory.
\item \$10 monthly for teachers (1,000 students, \$10 annually \$140,000) increased storage for improved inventory.
\end{itemize}
\textbf{Special Issues or Constraints:}
\begin{itemize}
\item We believe this to a strategic system. This web system would only be the beginning as we would be looking to create an application that would be more mobile friendly. This should raise more of an awareness within the students of EUC and also other students/teachers in Cyprus. students can also get more involved with University activities such as word based games, trivia etc.
\item This system should be in place by fall semester 2020.
\end{itemize}

\textbf{Requirements Elicitation / Requirements Definition}\\
In this section you should include the following:
\begin{itemize}
\item Business needs; \\ \textbf {Design:} We would be working directly with our University EUC so our design would range between our red white and black, our logo stays the same, we have our we our website being the major platform for our students and an app for other university students to log onto and have access to our books and products. Having this would cost illustrious design would comes with its own cost.\\ \textbf {Marketing:} Customer acquisition and affiliate marketing is our way to reach people, with Cyprus being a small town, word of mouth alone helps us to reach people. However, our affiliate marketing strategy would solidify our online and offline PR making us the more favourable choice as opposed to every other book store out there.  \\ \textbf {Technology.} \\ \textbf {Returns}
\item System’s main features (functionality)
\item Expected benefits (value)
\item Describe which requirements elicitation technique or techniques you would follow to
extract the requirements for the system in question.
\end{itemize}
\end{document}